\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
%\usepackage{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeEducation}[5]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      {\small #3} & \textit{\small #4} \\
      \textit{#5} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSimpleItem}[1]{\item\small {#1} \vspace{-4pt}}

\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

%For the UPenn work ex
\newcommand{\resumeLongSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-1pt}
}

\newcommand{\resumeLongSubSubheading}[1]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{\small#1} \\
    \end{tabular*}\vspace{-5pt}
}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://sauravbose.github.io/}{\Large Saurav Bose}} & Email : \href{mailto:saurav.bose93@gmail.com}{saurav.bose93@gmail.com}\\
  \href{https://sauravbose.github.io/}{https://sauravbose.github.io} & Mobile : +1-267-746-9451 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeEducation
      {University of Pennsylvania}{Philadelphia, PA}
      {Dual Master of Science in Scientific Computing and Mechanical Engineering;  GPA: 3.8/4.0}{2015 -- 2018}
      {Concentration in Statistics, Machine Learning and Numerical Analysis}
    \resumeEducation
      {National Institute of Technology Karnataka}{Surathkal, India}
      {Bachelor of Technology in Mechanical Engineering;  GPA: 8.8/10.0}{2011 -- 2015}{Concentration in Numerical Analysis and Simulation}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Children's Hospital of Philadelphia Research Institute}{Philadelphia, PA}
      {Data Scientist I}{Jul 2018 - Present}
      \resumeItemListStart
        \resumeSimpleItem
        {Led applied machine learning projects to predict various clinical outcomes using large scale EHR data from ideation to dissemination (see Publications).
        }
        \resumeSimpleItem
        {Formulated analysis plans in collaboration with physicians and other domain experts.
        }
        \resumeSimpleItem
        {Presented research findings to varied technical and non-technical audiences.
        }
        \resumeSimpleItem
        {Provided technical mentorship to students and fellow data scientists. 
        }
      \resumeItemListEnd
      
% --------Multiple Positions Heading------------
    % \resumeSubSubheading
    % {Software Engineer I}{Oct 2014 - Sep 2016}
    % \resumeItemListStart
    %     \resumeItem{Apache Beam}
    %      {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
    % \resumeItemListEnd
    % \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeLongSubheading
      {University of Pennsylvania}{Philadelphia, PA}
      {Graduate Research and Teaching Assistant}{May 2016 - May 2018}
      \resumeLongSubSubheading
        {Research}
      \resumeItemListStart
        \resumeSimpleItem
          {Worked with the School of Medicine and the School of Engineering on multiple research projects (see Portfolio for more details).}
        \resumeSimpleItem
          {Extended core Relief Based Algorithms (RBAs) for feature selection to their iterative variants suitable for Big Data applications. Made open-source contributions to scikit-rebate (a scikit-learn package under active development).}
        \resumeSimpleItem
          {Developed C/C++ codes implementing variations to Metropolis Monte Carlo algorithm for parametric estimation of molecular properties of fluids.}
      \resumeItemListEnd
      
      \resumeLongSubSubheading
        {Teaching}    
      \resumeItemListStart
        \resumeSimpleItem
          {Head TA at the Wharton School for Mathematical Statistics (Prof. Warren Ewens).}
        \resumeSimpleItem
          {TA at the Engineering School for advanced Machine Learning (Prof. Shivani Agarwal).}
        \resumeSimpleItem
          {Conducted office hours, tutorial sessions and mentored student projects.}
          
      \resumeItemListEnd

    \resumeSubheading
      {Avis Budget Group}{Parsippany, NJ}
      {Data Science Intern}{Summer 2017}
      \resumeItemListStart
        \resumeSimpleItem
        {Queried, cleaned and visualized corporate data from Oracle databases to automate demand and performance reporting processes.
        }
        \resumeSimpleItem
        {Developed an ensemble of Regularized Multiple Regression and Time Series models to predict rental demand.
        }
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------Publications-----------------
\section{Publications}
  \resumeSubHeadingListStart
    \resumeSimpleItem
    {\textbf{Bose, S.}, Kenyon, C. \& Masino, A.J. "Personalized Prediction of Early Childhood Asthma Persistence: A Machine Learning Approach", \textit{Under Review}
    }
    \resumeSimpleItem
    {Urbanowicz, R.J., Xu, A., \textbf{Bose, S.}, Orzechowski, P., Fu, W. \& Moore, J.H. "Scaling Advanced Feature Selection Methods for Biomedical Informatics and Beyond", \textit{In Preparation}
    }
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
    \resumeSubItem{Programming}
      {Python, R, SQL, C++, MATLAB}
    \resumeSubItem{Tools and Technologies}
      {PyTorch, GCP, Git, Docker, Tableau}
 \resumeSubHeadingListEnd

%--------Coursework------------
\section{Relevant Coursework}
Machine Learning, Big Data Analytics, Mathematical Statistics, Modern Data Mining, Data Science for Bioinformatics, Analysis of Algorithms, Numerical Methods, Probability Theory and Applications, Linear Algebra, Single and Multi-variable Calculus. 

%-------------------------------------------
\end{document}
